Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-12 manuscript.Rnw
Table with collaborators. Couple of small glitches but not bad. Closes #1

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
% \usepackage[T1]{fontenc}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
\usepackage{lineno}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\bibliographystyle{plain}

@@

\affil[1]{Hawkesbury Institute for the Environment}
\affil[2]{Macquarie University}
\affil[3]{See Supporting Information}

@@

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
source("R/functions-ms.R")
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS1b.pdf}
    \caption{Mean annual precipitation (MAP) and temperature (MAT) for all contributed datasets, by vegetation type. MAP and MAT were taken from Worldclim \cite{worldclim}, using latitude and longitude reported for each contributed dataset.}
    \label{fig:figureS1}
\end{figure}

@@

@@

<<>>=
@

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
% \usepackage[T1]{fontenc}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{lineno}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\bibliographystyle{plain}

@@

\affil[1]{1 Hawkesbury Insitute for the Environment, University of Western Sydney, Hawkesbury Campus, First Floor, Building L9, Locked Bag 1797, Penrith NSW 2751, Australia}
\affil[2]{Biological Sciences, Macquarie University NSW 2109, Australia}
\affil[3]{See Supporting Information}

@@

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
source("R/functions-ms.R")
baad <- readRDS("data/baad.rds")
dataauthors <- author_details(baad)
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS1.pdf}
    \caption{Mean annual precipitation (MAP) and temperature (MAT) for all contributed datasets, by vegetation type. MAP and MAT were taken from Worldclim \cite{worldclim}, using latitude and longitude reported for each contributed dataset.}
    \label{fig:figureS1}
\end{figure}

@@

<<results='asis'>>=
print(xtable(dataauthors,
             caption="Contributors to the BAAD"
             ), include.rownames=FALSE, tabular.environment='longtable', floating=FALSE, size="small",
      caption.placement="top")
@

@@
